---
title: "GSE146596_4datasets"
author: "Yifang Liu"
date: "`r Sys.Date()`"
output:
  rmdformats::html_clean:
    code_folding: hide
    fig_width: 10
    fig_height: 10
    highlight: kate
    thumbnails: false
    lightbox: true
    gallery: true
---

```{r knitr_init, echo=FALSE, cache=FALSE}
library(knitr)
library(rmdformats)

options(max.print = 200)
opts_chunk$set(echo = TRUE,
               cache = FALSE,
               prompt = FALSE,
               tidy = TRUE,
               comment = NA,
               message = FALSE,
               warning = FALSE,
               dev = c("png", "pdf"),
               fig.width = 10,
               fig.height = 10,
               fig.align = "center",
               # fig.path = '../Result/PDFs_/',
               dpi = 72)
opts_knit$set(width = 75)
```

```{r setup}
set.seed(123)

options(stringsAsFactors = FALSE)

results <- "../results/"
if (!dir.exists(results)) {dir.create(results)}

suppressPackageStartupMessages({
  library(Matrix)
  library(tidyverse)
  library(Seurat)
  library(GEOquery)
})
```

# Updated version with the following updates:

2020-07-28:

  * Export 4 datasets.

```{r download_data}
raw_data <- "../raw_data/"
if (!dir.exists(raw_data)) {dir.create(raw_data)}

GSE <- "GSE146596"
# geo <- getGEOSuppFiles(GSE, makeDirectory = FALSE, baseDir = raw_data)

Species <- "Drosophila"
Tissue <- "Blood"
```

```{r load_data}
seuratObj_origin <- readRDS("../raw_data/PlanC_blood_191012.Rds")
```

```{r combine}
sample <- "combine"

seuratObj <- seuratObj_origin

DefaultAssay(seuratObj) <- "RNA"
selected_res <- "merge_cluster"
Idents(seuratObj) <- selected_res

clusterMetadataTable <- table(seuratObj@meta.data[ , selected_res]) %>% as.data.frame()
colnames(clusterMetadataTable) <- c("celltype_id", "count")

# export clusterMetadataTable
write.csv(clusterMetadataTable,
          file = paste0(results, GSE, "_", sample, "_clusterMetadataTable_", Species, "_", Tissue, ".csv"),
          row.names = FALSE)

# extract data matrix from DotPlot function
all_genes <- rownames(seuratObj)
dot <- DotPlot(object = seuratObj, features = all_genes)
gene2clusterTable <- dot$data
colnames(gene2clusterTable) <- c("avg_exp", "pct_exp", "gene", "celltype_id", "avg_exp_scaled")

# export gene2clusterTable
write.csv(gene2clusterTable,
          file = paste0(results, GSE, "_", sample, "_gene2clusterTable_", Species, "_", Tissue, ".csv"),
          row.names = FALSE)
```

```{r UNinjured}
sample <- "UNwounded"

seuratObj <- seuratObj_origin

Idents(seuratObj) <- "Sample"
seuratObj <- subset(seuratObj, idents = "UNinjured")

DefaultAssay(seuratObj) <- "RNA"
selected_res <- "merge_cluster"
Idents(seuratObj) <- selected_res

clusterMetadataTable <- table(seuratObj@meta.data[ , selected_res]) %>% as.data.frame()
colnames(clusterMetadataTable) <- c("celltype_id", "count")

# export clusterMetadataTable
write.csv(clusterMetadataTable,
          file = paste0(results, GSE, "_", sample, "_clusterMetadataTable_", Species, "_", Tissue, ".csv"),
          row.names = FALSE)

# extract data matrix from DotPlot function
all_genes <- rownames(seuratObj)
dot <- DotPlot(object = seuratObj, features = all_genes)
gene2clusterTable <- dot$data
colnames(gene2clusterTable) <- c("avg_exp", "pct_exp", "gene", "celltype_id", "avg_exp_scaled")

# export gene2clusterTable
write.csv(gene2clusterTable,
          file = paste0(results, GSE, "_", sample, "_gene2clusterTable_", Species, "_", Tissue, ".csv"),
          row.names = FALSE)
```

```{r injured}
sample <- "wounded"

seuratObj <- seuratObj_origin

Idents(seuratObj) <- "Sample"
seuratObj <- subset(seuratObj, idents = "injured")

DefaultAssay(seuratObj) <- "RNA"
selected_res <- "merge_cluster"
Idents(seuratObj) <- selected_res

clusterMetadataTable <- table(seuratObj@meta.data[ , selected_res]) %>% as.data.frame()
colnames(clusterMetadataTable) <- c("celltype_id", "count")

# export clusterMetadataTable
write.csv(clusterMetadataTable,
          file = paste0(results, GSE, "_", sample, "_clusterMetadataTable_", Species, "_", Tissue, ".csv"),
          row.names = FALSE)

# extract data matrix from DotPlot function
all_genes <- rownames(seuratObj)
dot <- DotPlot(object = seuratObj, features = all_genes)
gene2clusterTable <- dot$data
colnames(gene2clusterTable) <- c("avg_exp", "pct_exp", "gene", "celltype_id", "avg_exp_scaled")

# export gene2clusterTable
write.csv(gene2clusterTable,
          file = paste0(results, GSE, "_", sample, "_gene2clusterTable_", Species, "_", Tissue, ".csv"),
          row.names = FALSE)
```

```{r WASP96hr}
sample <- "WASP96hr"

seuratObj <- seuratObj_origin

Idents(seuratObj) <- "Sample"
seuratObj <- subset(seuratObj, idents = "WASP96hr")

DefaultAssay(seuratObj) <- "RNA"
selected_res <- "merge_cluster"
Idents(seuratObj) <- selected_res

clusterMetadataTable <- table(seuratObj@meta.data[ , selected_res]) %>% as.data.frame()
colnames(clusterMetadataTable) <- c("celltype_id", "count")

# export clusterMetadataTable
write.csv(clusterMetadataTable,
          file = paste0(results, GSE, "_", sample, "_clusterMetadataTable_", Species, "_", Tissue, ".csv"),
          row.names = FALSE)

# extract data matrix from DotPlot function
all_genes <- rownames(seuratObj)
dot <- DotPlot(object = seuratObj, features = all_genes)
gene2clusterTable <- dot$data
colnames(gene2clusterTable) <- c("avg_exp", "pct_exp", "gene", "celltype_id", "avg_exp_scaled")

# export gene2clusterTable
write.csv(gene2clusterTable,
          file = paste0(results, GSE, "_", sample, "_gene2clusterTable_", Species, "_", Tissue, ".csv"),
          row.names = FALSE)
```

# Notes

2020-06-15:

  * Prepare data for CLP

2020-04-12:

  * Heatmap expression averaged by condition planC.

Wed Dec 4, 2019:

  * compatible to preview.

Tue Nov 5, 2019:

  * the heatmaps of the rest of the cluster from PlanC.

Thu Oct 31, 2019:

  * planC cluster11 markers v2 order by expression.

Wed Oct 30, 2019:

  * DEG with the heat map method for every condition in each cluster.

Wed Oct 23, 2019:

  * add injured vs WASP96hr.

Tue Oct 22, 2019:

  * planC Identify differential expressed genes across conditions v3 top5 top10 orderby logFC.

Fri Oct 18, 2019:

  * Dot Plots (separate pdfs for a, b, c) for the following genes from planC.

Wed Oct 16, 2019:

  * Dot plot of planC with reverse order... meaning cluster 0 on top....last cluster bottom.

Sun Oct 13, 2019:

  * add dot plots: Top three markers per clusters including the split (per condition); add corresponding heat maps.

Sat Oct 12, 2019:

  * The pdfs and pngs of Uninjured, injured, WASP96hr and All of them together (Merge) for the planC tSNE.

Wed Sep 11, 2019:

  * planC: merge cluster 0, 1, 14, 19 into 0.

Tuesday, August 27, 2019:

  * If a marker is already appeared in previous cluster, the follow up marker will be added, so that every cluster will have the same number of markers.

Monday, August 26, 2019:

  * Add marker genes, dotplot, heatmap.

Sunday, August 25, 2019:

  * If a gene express two out of three samples, we will keep these genes.

Friday, August 9, 2019:

  * Integrate analysis of UNinjured, injured and WASP96hr data, add Markers combined map.

Friday, August 2, 2019:

  * Split sample to different libraries, add QC, add combined map, change resolution (0.1 to 1).

Thursday, August 1, 2019:

  * Select the list of all cells of the 2 clusters (cluster 6 and 10) and do a clustering to see the sub-clusters.

Monday, July 29, 2019:

  * First version for integrate analysis of UNinjured injured WASP 10x indrop dropseq data.

# Session Info

```{r sessioninfo, message=TRUE}
sessionInfo()
```

